Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-05-02 WSSSPE4_report/wg_best_practices_sustainability.tex
trimmed people section in best practices/sustainability section

The people spearheading this effort at the time of the writing of this workshop report are Ray Idaszak <rayi@renci.org>, August Muench <august.muench@aas.org>, Jonah Miller <jmiller@perimeterinstitute.ca>, Lorraine Hwang <ljhwang@ucdavis.edu>, Peter Elmer <peter.elmer@cern.ch>, and Hans Fangohr <fangohr@soton.ac.uk>.

\noindent
Resources include research projects suggested from WSSSPE community including:
\begin{itemize}
\item FLASH (astrophysics, \url{http://flash.uchicago.edu/site/flashcode/})
\item GROMACS (chemistry, \url{http://www.gromacs.org/})
\item CIG (Earth science, \url{http://geodynamics.org/})
\item CUAHSI (Earth science, \url{https://www.cuahsi.org/})
\item CSDMS (Earth science, \url{https://csdms.colorado.edu/wiki/Main_Page})
\item OntoSoft (biology, \url{http://www.ontosoft.org/})
\item ASCL (astronomy, \url{http://ascl.net}), specifically ASCL entries sorted by citation count\footnote{\url{https://ui.adsabs.harvard.edu/\#search/q=bibstem\%3A\%22ASCL\%22&sort=citation_count\%20desc\%2C\%20bibcode\%20desc}}
\item yt-project (astronomy,  \url{http://yt-project.org})
\item Einstein Toolkit (physics, \url{https://einsteintoolkit.org/})
\item SpEC (physics, \url{https://www.black-holes.org/SpEC.html})
\item pyCLOUDY (astrophysics, \url{http://ascl.net/1304.020})
\end{itemize}

>>>>

The people spearheading this effort at the time of the writing of this workshop report are the
working group participants listed previously along with Peter Elmer <peter.elmer@cern.ch> and Hans Fangohr <fangohr@soton.ac.uk>.

Resources include research projects suggested from WSSSPE community including:
\begin{itemize}
\item FLASH (astrophysics, \url{http://flash.uchicago.edu/site/flashcode/})
\item GROMACS (chemistry, \url{http://www.gromacs.org/})
\item CIG (Earth science, \url{http://geodynamics.org/})
\item CUAHSI (Earth science, \url{https://www.cuahsi.org/})
\item CSDMS (Earth science, \url{https://csdms.colorado.edu/wiki/Main_Page})
\item OntoSoft (biology, \url{http://www.ontosoft.org/})
\item ASCL (astronomy, \url{http://ascl.net}), specifically ASCL entries sorted by citation count\footnote{\url{https://ui.adsabs.harvard.edu/\#search/q=bibstem\%3A\%22ASCL\%22&sort=citation_count\%20desc\%2C\%20bibcode\%20desc}}
\item yt-project (astronomy,  \url{http://yt-project.org})
\item Einstein Toolkit (physics, \url{https://einsteintoolkit.org/})
\item SpEC (physics, \url{https://www.black-holes.org/SpEC.html})
\item pyCLOUDY (astrophysics, \url{http://ascl.net/1304.020})
\end{itemize}
